Annotation exploration for SCPCP000006

### 2024-10-22 analyses/cell-type-wilms-tumor-06/notebook/04_annotation_Across_Samples_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook/04_annotation_Across_Samples_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

```{r fig.width=10, fig.height=4, out.width='100%'}
do_Feature_densityplot <- function(df, group.by, feature, split.by = NULL  ){

@@

Some cells have an excellent mapping score (>0,85) while other performed worth. Let's have a look at the repartiction per patient.

>>>>

```{r fig.width=10, fig.height=4, out.width='100%'}
do_Feature_densityplot <- function(df, group.by, feature){

@@

Some cells have an excellent mapping score (>0,85) while other performed worse. Let's have a look at the compartments per patient.
